\section{Preliminaries}
add intro text here
<no need to discuss same level as greg's paper>
1. graph
    a. what does this mean?
    	i. nodes <what does this mean>
    	ii. edges <what does this mean>
    b. associated variables
    c. accounting for bus schedule
    d. group constraints
        a. meaning
    e. graph encodes connection bus-battery charger connection opportunities
    f. incidence matrix + linear algebra
    g. show picture of graph
2. Battery SOC
    a. Introduce new variables d_{i,j} g_{i,j}
    b. charging
        i. variable rate
	ii. variable rate adds edges to the graph (contribution)
	iii. show picture with d_{i,j} illustrated
    c. discharging
        i. delta is all that matters
	ii. comes from sim/real data (contribution)
3. Rate schedule
    a. consumption
    b. power, average power, demand charge (abstract)
        i. peak vs facilities demand charge
	ii. constraints for this
4. Fleet Operations
    a. Depot for night time charging
        i. one charger per bus
	ii. slow chargers
	iii. single rate charging
    b. Station for daytime charging
        i. limited number of chargers
	ii. fast/variable rate
    c. multiple graphs
        i. interconnections through SOC variables
	ii. show picture for this
5. Objective Function
6. Gurobi
7. Results
8. Future Work

\input{preliminaries/Graph.tex}
\input{preliminaries/linearProgram.tex}
\input{preliminaries/batterySoc.tex}
\input{preliminaries/rateSchedule.tex}
\input{preliminaries/fleetOperations.tex}
